---
title: "Implementation of uncertainty analysis"
format: 
  html:
    page-layout: full
---
:::: {.panel-tabset}

## Video

<iframe width="560px" height="320px" allowfullscreen="true" allow="autoplay *" title="Sequence_01_Implementation" src="https://lu.instructuremedia.com/embed/cda3e254-e10f-41e0-9926-a139e149595f" frameborder="0"></iframe>

## Text

Welcome to the implementation page! 

Here we have collected some examples of scientific opinions and report which demonstrate how the guidances can be put into practice. 

You should not think of this list as recommendations or endorsements, but rather as a list of references or real-life examples of assessments, which contain certain aspects of the implementation of the guidance for uncertainty analysis or the guidance of communication of uncertainty.

The examples are reported in an interactive table which contains a list of scientific opinions organised by the Panel, and the type of assessment. 

This list is not exhaustive.

You can use the search bar to quickly subset this table by the uncertainty expression or the method of uncertainty analysis used in the assessment. 

Lastly, we provide the motivation for including the specific assessment in the list of examples. You can get to the full document text by clicking the link in the last column of the table. The link will take you to the location of the example in the document.

We hope you find these examples useful in your work!

Thank you!

::::

#### Examples of scientific reports and opinions implementing the Guidance on Uncertainty Analysis. 

Please use the &#8853; sign to unfold the comments section. Each line in the comment section corresponds to an expression or a method indicated for the selected scientific opinion. If you click on the method or expression you will be taken to a place in the opinion where this is used or described. 

Methods for uncertainty analysis are described in [Principles and Methods](principles-and-methods/methods.qmd) section. Expressions resulting from applying uncertainty analysis are described in the [Communication of Uncertainty](uncertainty-communication.qmd) section.

```{r}
#| label: readsheets
#| echo: false
#| warning: false
#| message: false
options(tidyverse.quiet=TRUE)
library(googlesheets4)
library(tidyverse)
library(htmltools)
library(DT)
sheet_id <- "1Ja2aKHBDSwVYOoaChP2a2apJoNDfUwyvg0TLcOlvlnw"
url_prefix <- "https://efsa.onlinelibrary.wiley.com/doi/"
ex_df <- googlesheets4::read_sheet(sheet_id, sheet="Examples")
ex_expr_df <- googlesheets4::read_sheet(sheet_id, sheet="ExamplesExpressions")
ex_meth_df <- googlesheets4::read_sheet(sheet_id, sheet="ExamplesMethods")
```

```{r}
#| label: impltable
#| echo: false
ex_html_meth_df <- ex_meth_df %>% 
    group_by(DOI) %>% 
  mutate(idx_Method = letters[seq_len(n())],
         Comment = paste0("<sup>", idx_Method, "</sup>", Comment),
         html_Method = purrr::map2_chr(Method, Link, 
                ~as.character(htmltools::a(.x, href=.y))),
         html_Method=paste0(html_Method, "<sup>", idx_Method, "</sup>")) %>% 
  summarise(html_Method=paste(html_Method, collapse = "</br>"),
            html_MethodComment=paste(Comment, collapse = "</br>")) 

ex_html_expr_df <- ex_expr_df %>% 
  group_by(DOI) %>% 
  mutate(idx_Expression = seq_len(n()),
         Comment = paste0("<sup>", idx_Expression, "</sup>", Comment),
    html_Expression=purrr::map2_chr(Expression, Link, 
          ~as.character(htmltools::a(.x, href=.y))),
    html_Expression=paste0(html_Expression, "<sup>", idx_Expression, "</sup>")) %>%
  summarise(html_Expression=paste(html_Expression, collapse = "</br>"),
            html_ExpressionComment=paste(Comment, collapse = "</br>"))

ex_df %>% 
  left_join(ex_html_expr_df, by="DOI") %>% 
  left_join(ex_html_meth_df, by="DOI") %>% 
  mutate(DOI=map_chr(DOI, 
    ~as.character(htmltools::a(.x, href=paste0(url_prefix, .x)))),
    Comment=paste0("<b>Expression:</b></br>", html_ExpressionComment,
                  "</br><b>Method:</b></br>",html_MethodComment)) %>% 
  select(DOI, Title, Panel, Type, 
         Expression=html_Expression, Method=html_Method, Comment) %>% 
  cbind(' ' = '&oplus;', .) %>% 
  DT::datatable(escape = FALSE, plugins = "ellipsis", rownames=FALSE,
      options=list(scrollX=TRUE,
        columnDefs=list(
          list(visible = FALSE, targets = c(7)),
          list(orderable = FALSE, className = 'details-control', targets = 0),
          list(targets=c(2), render=JS("$.fn.dataTable.render.ellipsis( 17, false )"))
                  )),
        callback=JS("
  table.column(1).nodes().to$().css({cursor: 'pointer'});
  var format = function(d) {
    return '<div style=\"background-color:#eee; padding: .5em;\">' +
            d[7] + '</div>';
  };
  table.on('click', 'td.details-control', function() {
    var td = $(this), row = table.row(td.closest('tr'));
    if (row.child.isShown()) {
      row.child.hide();
      td.html('&oplus;');
    } else {
      row.child(format(row.data())).show();
      td.html('&CircleMinus;');
    }
  });"
                ))
```

